---
title: "Cheatsheet R"
author: "Tatiana Aguilar"
date: "2023-01-22"
output: html_document
---

```{r}
library(tidyverse)
```

### To check what directory you're currently in (your working directory).
```{r}
getwd() #Just run this you don't have to add anything to the parenthesis
```

### If you need to run an expression just type it in, remeber that order of operations apply.

### '<-' is the symbol read as 'gets'

### In order to make a vector (a string of values) you have to store it as an object.
```{r}
object<- c(1, 4, 7, 8)
```

### To calculate mean
```{r}
mean(object)
```

### To calculate median
```{r}
median()
```

### To calculate standard deviation
```{r}
sd(object)
```

### If you need help with a command, typs ? in front of the command of interest.
```{r}
?sd
```

### To print an object just type the object's name
```{r}
object
```

### Operators
Less than <, Greater than >, Less than or equal to <=, Greater than or equal to >=, equal to ==.

### To get values and not the logical evaluation of the entire vector.
```{r}
object[object >= 7]
```

